Hydras and Cie (Draft) \\ Variations on Kirby \& Paris' hydra battles and ordinal numbers in Coq

### 2021-09-13 doc/JFLA2022/paper.tex
small corrections

%------------------------------------------------------------------------------
\section{Introduction}
\label{sect:introduction}
Hydra games (a.k.a. \emph{Hydra battles}) appear in an article published in 1982 by two mathematicians:
L. Kirby and J. Paris~\cite{KP82}: \emph{Accessible Independence Results for Peano Arithmetic}.
This article presents a gameful interpretation of accessibility problem in the set of ordinals below $\epsilon_0$, and proves two theorems:
\begin{quote}
\begin{itemize}
\item In the Hydra game, every strategy is a winning strategy for Hercules.
  \item The theorem above cannot be proved in Peano Arithmettic.
\end{itemize}
\end{quote}

@@

Our proof is very different from the computational proof of Fig\ref{fig:Ex42E0}.
By definition of additive principal ordinals, 
it suffices to prove the inequality $\omega+42< \phi_0(2)$ to  fprove our lemma.

>>>>

%------------------------------------------------------------------------------
\section{Introduction}
\label{sect:introduction}
Hydra games (a.k.a. \emph{Hydra battles}) appear in an article published in 1982 by two mathematicians:
L. Kirby and J. Paris~\cite{KP82}: \emph{Accessible Independence Results for Peano Arithmetic}.
This article presents a gameful interpretation of accessibility problem in the set of ordinals below $\epsilon_0$, and proves two theorems:
\begin{quote}
\begin{description}
\item[$(1)$] In the Hydra game, every strategy is a winning strategy for Hercules.
  \item[$(2)$] The theorem $(1)$ cannot be proved in Peano Arithmetic.
\end{description}
\end{quote}

@@

Our proof is very different from the computational proof of Fig\ref{fig:Ex42E0}.
By definition of additive principal ordinals, 
it suffices to prove the inequality $\omega+42< \phi_0(2)$.
